\bf Faster Neural Machine Translation Inference

### 2018-02-16 fast-beam/fast-beam.tex
fast beam paper
fast paper

\Comment{calculate softmax}
\ForAll{$p_i$ in $p$}
  \State $p_i \gets \frac{\exp(p_i) - max}{sum} $
\EndFor

@@

\Procedure{Find-Best}{softmax vector $p$}

@@

@@

As can be seen, the operations iterate over the matrix p five times - once to add the bias, three times to calculate the softmax, and once to search for the best class. We fuse the three operation into one kernel, a popular optimization technique~\citep{Guevara2009EnablingTP}.

Secondly, we make use of the fact that softmax and $\exp$ are monotonic functions therefore we can move the search for the best class from FIND-BEST to SOFTMAX.

Thirdly, we are only interested in the probabilities of the best classes. Since these classes are known, we can avoid calculating softmax for all classes. The outline of the our function is shown in Algorithm~\ref{algo:Fused Kernel}.

>>>>

\Comment{calculate softmax}
\ForAll{$p_i$ in $p$}
  \State $p_i \gets \frac{\exp(p_i - max)}{sum} $
\EndFor

@@

\Procedure{Find-Best}{vector $p$}

@@

\Return $max$, $best$

@@

As can be seen, the matrix p is iterated over five times - once to add the bias, three times to calculate the softmax, and once to search for the best class. We fuse the three functions into one kernel, a popular optimization technique~\citep{Guevara2009EnablingTP}, making use of the following observations.

Firstly, softmax and $\exp$ are monotonic functions, therefore, we can move the search for the best class from FIND-BEST to SOFTMAX, at the start of the kernel.

Secondly, we are only interested in the probabilities of the best classes. Since they are now known at the start of the kernel, we compute softmax only for those classes. The outline of the our function is shown in Algorithm~\ref{algo:Fused Kernel}.
